How has the Brazilian Amazon been constructed as a problem:presidential speeches and transnational politics since 1985

### 2023-01-26 Submission/Re-submission/draft/draft_resubmission.rmd
facete outcome and setting

mmt1 <- ama_mx %>%
  filter(mx_cat2 == "Mixed-types") %>%
  count(mx_cat) %>%
  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
mmt2 <- ama_mx %>%
  count(mx_cat)%>%
  mutate(perc = n / sum(n)) # averages in relation to full sample
ama_mx %>%
  count(mx_cat, mx_cat2, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>%
  filter(mx_cat=="Pure Environmental Conservation" | mx_cat=="Pure Economic Integration")%>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc),
              se = FALSE, linewidth =0.75, linetype="solid", color="black") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Relationship between problem-constructions and deforestation rates",
       subtitle = "Bars indicated yearly deforestation level and curves indicated yearly share of problem-construction.",
       caption = "Curves in the plot were smoothed using loess method.")+
  theme_am()+
  facet_wrap("mx_cat") +
  geom_col(amazon_def_year, mapping = aes(x = year, y = def_year/80,fill=extremes),alpha=.5)+
  scale_fill_manual(values=c("lightgrey", "darkolivegreen"))+
  annotate("text", x = 2008, y = 0.35, label = "27'772 km2\ndeforested" , size = 3, color="darkolivegreen", face="bold")+
  annotate("text", x = 2016, y = 0.05, label = "4'571 km2\ndeforested", size = 3, color="darkolivegreen", face="bold")

```

>>>>

ama_mx %>%
  count(mx_cat, mx_cat2,location_cat, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(location_cat=="Amazonian States"|location_cat=="International")%>%
  filter(mx_cat2 == "Pure-types") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, fill=),
              se = FALSE, linewidth =0.75, linetype="solid", color="black") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+
  facet_wrap(~location_cat+mx_cat, nrow=2)+
  labs(x = "", y = "", title ="Relationship between problem-constructions and deforestation rates",
       subtitle = "Bars indicated yearly deforestation level and curves indicated yearly share of problem-construction.",
       caption = "Curves in the plot were smoothed using loess method.")+
  theme_am()+
  geom_col(amazon_def_year, mapping = aes(x = year, y = def_year/80,fill=extremes),alpha=.5)+
  scale_fill_manual(values=c("lightgrey", "darkolivegreen"))+
  annotate("text", x = 2008, y = 0.35, label = "27'772 km2\ndeforested" , size = 3, color="darkolivegreen", face="bold")+
  annotate("text", x = 2016, y = 0.05, label = "4'571 km2\ndeforested", size = 3, color="darkolivegreen", face="bold")
```
